Verifying Demonstrations

### 2020-02-12 paper/DBSchnorr-n-bit.tex
Minor clarifications for l-bit reduction to DLP
Minor rephrasing about relation between DBSP and DLP

The adversary has a commitment to the randomness~\(r_i\) in the form of \(R_i = 
g^{r_i}\) and a commitment to \(\alpha\) in the form of \(A = g^\alpha\).
This means that
\begin{align*}
  R = A^{-c'} g^{s'} &= A^{-c'} g^{s'[0] 2^0 + \dotsb + s'[m-1] 2^{m-1}} \\
                     &= A^{-c'} g^{s'[0] 2^0} \dotsb g^{s'[m-1] 2^{m-1}} \\
                     &= A^{-c'} g^{s'_{\text{known}}} g^{s'_{\text{unknown}}}.
\end{align*}
We will now show that finding \(s'_\text{unknown}\) is as hard as finding 
discrete logarithms.

@@

\begin{lemma}
  Given an algorithm~\(\algA_{\DBS}\) that solves the DB-Schnorr Problem 
  (\cref{DBSchnorr-problem}) with probability \(\epsilon\), we can construct an 
  algorithm \(\algA_{\text{DL}}\) that solves the \ac{DLP} with probability 
  \(\epsilon 2^{-l-k}\).
\end{lemma}

@@

  If \(A_{\text{DL}} = g^{\alpha_{\text{DL}}}\) is chosen such that 
  \(\alpha_{\text{DL}}\) has the \(l\) least significant bits set to zero 
  (probability \(2^{-l}\)), then will have \(
    \alpha_{\text{DL}}\gets \algA_{\DBS}(g, q, A_{\DBS}, \hat R, \hat s)
  \) with probability \(\epsilon\).
  Thus, the total probability of success is \(
    \epsilon 2^{-l} 2^{-k} = \epsilon 2^{-l-k}.
  \)
\end{proof}

>>>>

The adversary has a commitment to the randomness~\(r_i\) in the form of \(R_i = 
g^{r_i}\) and a commitment to \(\alpha\) in the form of \(A = g^\alpha\).
This means that
\begin{align*}
  R = A^{-c'} g^{s'} &= A^{-c'} g^{s'[0] 2^0 + \dotsb + s'[m-1] 2^{m-1}} \\
                     &= A^{-c'} g^{s'[0] 2^0} \dotsb g^{s'[m-1] 2^{m-1}} \\
                     &= A^{-c'} g^{s'_{\text{known}}} g^{s'_{\text{unknown}}}.
\end{align*}
We will now show how the hardenss of finding \(s'_\text{unknown}\) relates to 
the hardness of finding discrete logarithms.

@@

\begin{lemma}
  Given an algorithm~\(\algA_{\DBS}\) that solves the DB-Schnorr Problem 
  (\cref{DBSchnorr-problem}) with probability \(\epsilon\), we can construct an 
  algorithm \(\algA_{\text{DL}}\) that solves the \ac{DLP} with probability 
  \(\epsilon 2^{-(l+k)}\).
\end{lemma}

@@

  If \(A_{\text{DL}} = g^{\alpha_{\text{DL}}}\) is chosen such that 
  \(\alpha_{\text{DL}}\) has the \(l\) least significant bits set to zero 
  (probability \(2^{-l}\)), then will have \(
    \alpha_{\text{DL}}\gets \algA_{\DBS}(g, q, A_{\DBS}, \hat R, \hat s)
  \) with probability \(\epsilon\).
  Thus, the total probability of success is \(
    \epsilon 2^{-l} 2^{-k} = \epsilon 2^{-(l+k)}.
  \)
\end{proof}

As mentioned above, both \(l\) and \(k\) are logarithmic in the security 
parameter.
